%
% Copyright (c) 1996 Bunyip Information Systems Inc.
% All rights reserved
%
% Archie 3.5
% August 1996
%
% intro.tex
%

\chapter{Introduction}

\pagenumbering{arabic}
\setcounter{page}{1}


It was inevitable that the technology under which Archie was built changed.
With the introduction of faster applications and newer media on the Internet,
Archie had to reshape its structure to accomodate these new factors and
stay in the race.

Speed in this day and age is a big gain and Archie is thought to have
achieved it with the utilization of a string indexing tree for faster string
searches.

As for the World Wide Web and its many new faces, Archie also introduces its
latest web crawling and indexing engine.  In addition, a new web interface has
been added to accomodate the web users.  And with a few more newly added
features and face-lifts, Archie v3.5 is ready to undergo deployment.

This manual is an attempt to clarify the many components of Archie v3.5 and
its functionality.  Please keep in mind that this manual is also undergoing
changes, so we appreciate any comments sent to archie-group@bunyip.com.

What follows is the list of added features in Archie v3.5. You will find in
the table of contents, symbols such as the one in the margin, to help you
find the relevant documentation concerning the new features. \New

\begin{itemize}
\item Support for a new database module (webindex):
  \begin{itemize}
    \item Retrieval of HTML pages through HTTP protocol.
    \item Keyword extraction.
    \item Controlled crawling of the WWW.
    \item Site by site basis.
    \item Content extraction.
    \item Configurable stoplist (keyword exclusion).
  \end{itemize}
\item New database structure:
  \begin{itemize}
    \item A more reliable and independent database structure. 
  \end{itemize}
\item New strings search engine:
  \begin{itemize}
    \item Based on a paged, tree structured strings index.
    \item Faster searches.
    \item Less memory required.
    \item More disk space needed for construction of the index.
  \end{itemize}
\item New search interface:
  \begin{itemize}
    \item New WWW (CGI compliant) front-end to the Archie database.
  \end{itemize}
\item A better domain filter for any database:
  \begin{itemize}
    \item Results can be pre-configured to return in a certain order (e.g. FTP sites closest to the server first).
    \item Configurable on a server basis.
  \end{itemize}
\item General new features:
  \begin{itemize}
    \item Support for ls-lR.gz files.
    \item ISO-Latin-1 support for searches.
  \end{itemize}
\end{itemize}



\section{Future}

We hope in the very near future to be able to produce
the following list of features. If you have any suggestions
to add to the list please feel free to contact us at
archie-group@bunyip.com:

\begin{itemize}
  \item  Search tools:
    \begin{itemize}
      \item Add boolean searches.
      \item Allow other types of searches. (For example, return a
            list of hosts in any database and when they were last updated.)
      \item Multi-lingual Web front-end.
    \end{itemize}
  \item  Database:
    \begin{itemize}
      \item  An automated check-up program that runs periodically on the
             databases.  It will check the consistency of the database and
             fix any errors it runs into.   This will reduce the amount of
             time an Archie administrator needs to spend maintaining an Archie server.
      \item  Improve on filters and parsers to handle strange and unusual site
             listings.
      \item  Parallelize the parsing and updating of different databases.
      \item  Build multiple databses with the same access method.
    \end{itemize}
  \item  Management tools:
    \begin{itemize}
      \item  CGI web interface to allow web and FTP administrators to register
             their sites automatically.
      \item  Replace ``host\_manage'' with a new method for managing the
             host\_db database.
      \item  Statistical tools.
    \end{itemize}
\end{itemize}

